### 2018-03-28 air_gyroscope/paper.tex
Script + paper

	HEY SORRY FOR CAPS COULD YOU PLEASE TRY TO KEEP ``OBSERVATIONS'' RIGHT AT THE TOP OF PAGE TWO? THANKS

@@

	The change in the angular momentum vector of the rotor arises from a torque acting in the horizontal plane resulting from the imbalance from the truncated section of the sphere. A pure precession about a vertical axis arises due to the fact that the torque is at all times perpendicular to the angular momentum.

@@

	Conclusion goes here

>>>>

	The precession of an air gyroscope is a simple yet an accurate way of approximating the value of \textit{g}, the acceleration due to gravity. This paper outlines the experimental setup as well as some necessary derivations. Upon implementing the procedure, \( g \) is determined to be \( \pars{9.79 \pm .02} \si{\metre\per\second\squared} \), agreeing with the actual value.

@@

	The change in the angular momentum vector of the rotor arises from a torque acting in the horizontal plane result5ing from the imbalance from the truncated section of the sphere. A pure precession about a vertical axis arises due to the fact that the torque is at all times perpendicular to the angular momentum.

@@

	This experiment has shown that a simple setup designed to observe the precession of an air gyroscope could be used to accurately determine the value of \textit{g}. Specifically, acceleration due to gravity was determined to be \( \pars{9.79 \pm .02} \si{\metre\per\second\squared} \), agreeing with the actual value.

	Various sources of possible error may arise as one implements the procedure outlined in this experiment. For instance, upon obtaining the desired frequency of rotation of the truncated sphere, the first few rotations could be affected by the still-significant transients in the motion. This could be reflected in measurements in the form of a shorter period of rotation. Additionally, one's control of air flow is limited and is assumed to remain constant throughout the course of the experiment. Finally, some error could arise from numerical approximations of integrals, but it remains nearly insignificant when compared to other sources.
